(15 marks) Answer the following questions briefly
\begin{enumerate}
\item Does every closed 2D manifold necessarily divide the space into an inside and an outside? Justify your answer. \\
No - For example the mobious strip. It only has a single side, making it rather hard to distinguish between inside/outside. Especially as at a particular segment or if cut in half, it appears to have two sides.\\

\item Show that general cones and general cylinders are special cases of Coons surfaces. \\
As we are aware a generalized cone is a subset of a ruled surface, and as is generalized cylinder, if we show that a coon can represent a given ruled surface, we have shown it can make generalized cones/cylinders. \\

A ruled surface is parameterized as follows: $Q(u,v) = (1 - v)P_0(u) + vP_1(u)$. \\
Where as a Coons Patch can be expressed as: $Q(u, v) =$ \\
$[Q_0 (v)(1 - u) + Q_1 (v)u]$ (the first ruled surface) \\
$+ [P_0 (u)(1 - v) + P_1 (u)v]$ (the second ruled surface) \\
$- [(1 - u)(1 - v)P_{00} + u(1 - v)P_{01} + (1 - u)vP_{10} + uvP_{11} ]$ (The bi-linear patch) \\

If we define $P_0(u) = (1-u)P_{00} + uP_{01}$ \\
If we define $P_1(u) = (1-u)P_{10} + uP_{11}$ \\
we get: \\
$Q_o(v)(1u) + Q_1(v)(u)$ \\
as the remaining terms cancel out:
\begin{align*}
[P_0 (u)(1 - v) + P_1 (u)v] &= \\
&= (1-v)((1-u)P_{00} + uP_{01}) + v((1-u)P_{10} + uP_{11}) \\
&= [(1 - u)(1 - v)P_{00} + u(1 - v)P_{01} + (1 - u)vP_{10} + uvP_{11} ]
\end{align*}
Which is what is being subtracted as the last term/bilinear patch, canceling it out.

\item Find a set of subdivision filters that guarantees C 4 continuity. You may ignore boundary
conditions. \\
(1/32)(1,6,15,20,15,6,1) \\
Generated via pascals triangle and the properties of general B-spline. \\
The pascal triangle /$(2^n)$, where n is the layer down in pascal triangle (with a slight offset), is just a pattern recognized to match the B-spline's filters, as discussed in class and in the notes. And as these are the filters of B-splines, we need an order 7 B-spline, which is the row chosen here.
\end{enumerate}
